### 2021-04-23 2021.csic5011/homework/homework08.tex
Add files via upload

\item *{\em Niyogi-Smale-Weinberger Consistency Theorem.} The following theorem establishes the homology consistency of C\v{e}ch complex of discrete samples uniformly from a compact submanifold of $\R^d$. 
\paragraph{Theorem.}{} Let $M$ be a compact submanifold of $\mathbb{R}^{d}$ with condition number $\tau$ and let $\left\{x_{1}, \ldots, x_{n}\right\}$ be a set of points drawn from $M$ according to the volume measure. Fix $0<\epsilon<\frac{\tau}{2}$. Then if
$$
n>\beta_{1}\left(\log \left(\beta_{2}\right)+\log \left(\frac{1}{\delta}\right)\right),
$$
there is a homotopy equivalence
$$
\bigcup_{z \in\left\{x_{1}, \ldots, x_{n}\right\}} B_{\epsilon}(z) \simeq M
$$
between the union of balls and $M$ (and in particular the homology groups coincide) with probability $>1-\delta$.
Here
$$
\beta_{1}=\frac{\operatorname{vol}(M)}{\cos ^{d}\left(\theta_{1}\right) \operatorname{vol}\left(B_{\frac{\epsilon}{4}}^{d}\right)}
$$
and
$$
\beta_{2}=\frac{\operatorname{vol}(M)}{\cos ^{d}\left(\theta_{2}\right) \operatorname{vol}\left(B^d_{\frac{\epsilon}{8}} \right)},
$$
where $\theta_{1}=\arcsin \left(\frac{\epsilon}{8 \tau}\right), \theta_{2}=\arcsin \left(\frac{\epsilon}{16 \tau}\right)$, and $\operatorname{vol}\left(B_{r}^{d}\right)$ denotes the volume of the
$d$-dimensional ball of radius $r$.
\emph{Can you read the paper and sketch the main idea for the proof? What about the noisy samples near the submanifold? }
\paragraph{Reference:} Partha Niyogi, Stephen Smale, and Shmuel Weinberger. \emph{Finding the homology of submanifolds with high confidence from random samples}. Discrete Comput. Geom. 39(1-3): 419-441, 2008.
%\item {\em Mapper}: 
\end{enumerate}

>>>>

\item *{\em Niyogi-Smale-Weinberger Consistency Theorem.} The following theorem establishes the homology consistency of \v{C}ech complex of discrete samples uniformly from a compact submanifold of $\R^d$. 
\paragraph{Theorem.}{} Let $M$ be a compact submanifold of $\mathbb{R}^{d}$ with condition number $\tau$ and let $\left\{x_{1}, \ldots, x_{n}\right\}$ be a set of points drawn from $M$ according to the volume measure. Fix $0<\epsilon<\frac{\tau}{2}$. Then if
$$
n>\beta_{1}\left(\log \left(\beta_{2}\right)+\log \left(\frac{1}{\delta}\right)\right),
$$
there is a homotopy equivalence
$$
\bigcup_{z \in\left\{x_{1}, \ldots, x_{n}\right\}} B_{\epsilon}(z) \simeq M
$$
between the union of balls and $M$ (and in particular the homology groups coincide) with probability $>1-\delta$.
Here
$$
\beta_{1}=\frac{\operatorname{vol}(M)}{\cos ^{d}\left(\theta_{1}\right) \operatorname{vol}\left(B_{\frac{\epsilon}{4}}^{d}\right)}
$$
and
$$
\beta_{2}=\frac{\operatorname{vol}(M)}{\cos ^{d}\left(\theta_{2}\right) \operatorname{vol}\left(B^d_{\frac{\epsilon}{8}} \right)},
$$
where $\theta_{1}=\arcsin \left(\frac{\epsilon}{8 \tau}\right), \theta_{2}=\arcsin \left(\frac{\epsilon}{16 \tau}\right)$, and $\operatorname{vol}\left(B_{r}^{d}\right)$ denotes the volume of the
$d$-dimensional ball of radius $r$.
\emph{Can you read the paper and sketch the main idea for the proof? What about the noisy samples near the submanifold? }
\paragraph{Reference:} Partha Niyogi, Stephen Smale, and Shmuel Weinberger. \emph{Finding the homology of submanifolds with high confidence from random samples}. Discrete Comput. Geom. 39(1-3): 419-441, 2008.
%\item {\em Mapper}: 
\end{enumerate}
